Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-09-03 paper.tex
changeto secind sentence of Introduction (test edit & commit)

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically similar in scale if certain nondimensional
physical parameters are matched. In the case of fluid systems, the most
important parameter is often the Reynolds number, which quantifies the
importance of viscosity on the flow physics. As such, hereafter we will use the
word ``scale'' to refer to this dynamical scale rather than the geometric scale.

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically identical in scale if certain nondimensional
physical parameters are matched. In the case of fluid systems, the most
important nondimensional parameter is often the Reynolds number, which
quantifies the importance of inertial forces over viscous forces on the flow
physics. It should be noted that in general the geometric scale of a physical
model is not necessarily the same as its dynamical scale. In the case of
geometrically similar physical models of turbines and propellers operating under
kinematic similarity, i.e. at the same tip speed or advance ratio, however, the
dynamical scale can be (is) the same as the geometric scale. It is the dynamical
scale of the model which we are concerned with hereafter.

\todo[inline]{Need to find a good way to succintly introduce scaling 
subleties.}
